\begin{thebibliography}{99}
    \bibitem[Analytics(2022)]{realtime_analytics}
    Analytics (2022).
    \newblock {Real-time Analytics: Definition, Examples, and Use Cases}.
    \newblock \url{https://www.databricks.com/glossary/real-time-analytics}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Processing(2022)]{data_processing_models}
    Processing (2022).
    \newblock {Data Processing Models: Batch vs. Stream Processing}.
    \newblock \url{https://www.confluent.io/learn/batch-vs-real-time-data-processing/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Challenges(2022)]{realtime_challenges}
    Challenges (2022).
    \newblock {Challenges in Real-time Data Processing}.
    \newblock \url{https://www.infoq.com/articles/real-time-data-processing-challenges/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Systems(2022)]{multisensor_systems}
    Systems (2022).
    \newblock {Multi-sensor Systems in Industrial Applications}.
    \newblock \url{https://www.sciencedirect.com/science/article/pii/S2405896318332421}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Sensors(2022)]{industrial_sensors}
    Sensors (2022).
    \newblock {Industrial Sensors and Their Applications}.
    \newblock \url{https://www.omega.com/en-us/resources/industrial-sensors}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Architecture(2022)]{multisensor_architecture}
    Architecture (2022).
    \newblock {Multi-sensor System Architecture and Design}.
    \newblock \url{https://www.mdpi.com/1424-8220/22/1/31}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Microservices(2022)]{microservice_architecture}
    Microservices (2022).
    \newblock {Pattern: Microservice Architecture}.
    \newblock \url{https://microservices.io/patterns/microservices.html}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Benefits(2022)]{microservice_benefits}
    Benefits (2022).
    \newblock {Benefits of Microservices Architecture}.
    \newblock \url{https://www.nginx.com/blog/introduction-to-microservices/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Challenges(2022)]{microservice_challenges}
    Challenges (2022).
    \newblock {Challenges in Microservices Architecture}.
    \newblock \url{https://www.nginx.com/blog/microservices-at-netflix-architectural-best-practices/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Kubernetes(2022)]{kubernetes}
    Kubernetes (2022).
    \newblock {Kubernetes Documentation}.
    \newblock \url{https://kubernetes.io/docs/home/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Concepts(2022)]{kubernetes_concepts}
    Concepts (2022).
    \newblock {Kubernetes Core Concepts}.
    \newblock \url{https://kubernetes.io/docs/concepts/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Benefits(2022)]{kubernetes_benefits}
    Benefits (2022).
    \newblock {Benefits of Using Kubernetes}.
    \newblock \url{https://kubernetes.io/docs/concepts/overview/what-is-kubernetes/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Kafka(2022)]{kafka}
    Kafka (2022).
    \newblock {Apache Kafka Documentation}.
    \newblock \url{https://kafka.apache.org/documentation/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Streams(2022)]{kafka_streams}
    Streams (2022).
    \newblock {Kafka Streams Documentation}.
    \newblock \url{https://kafka.apache.org/documentation/streams/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Flink(2022)]{flink}
    Flink (2022).
    \newblock {Apache Flink Documentation}.
    \newblock \url{https://flink.apache.org/docs/stable/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Streaming(2022)]{spark_streaming}
    Streaming (2022).
    \newblock {Spark Streaming Documentation}.
    \newblock \url{https://spark.apache.org/docs/latest/streaming-programming-guide.html}
    \newblock [Accessed: 01/01/2024].

    \bibitem[SCADA(2022)]{scada}
    SCADA (2022).
    \newblock {SCADA Systems: What They Are and How They Work}.
    \newblock \url{https://www.inductiveautomation.com/resources/article/what-is-scada}
    \newblock [Accessed: 01/01/2024].

    \bibitem[IoT(2022)]{cloud_iot}
    IoT (2022).
    \newblock {Cloud IoT Platforms Comparison}.
    \newblock \url{https://www.postscapes.com/internet-of-things-platforms/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Edge Computing(2022)]{edge_computing}
    Edge Computing in Industrial IoT (2022).
    \newblock \url{https://www.iiconsortium.org/pdf/IIC_Edge_Computing_in_IIoT_2019.pdf}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Open Source(2022)]{open_source_realtime}
    Open Source Real-time Analytics Tools (2022).
    \newblock \url{https://www.influxdata.com/blog/open-source-time-series-databases/}
    \newblock [Accessed: 01/01/2024].

    \bibitem[Nirmal et~al.(2016)]{imu_noise}
    Nirmal, K.~J., Mathew, J., Sreejith, A.~G., and Saprotdar, M. (2016).
    \newblock \emph{Noise modeling and analysis of an IMU-based attitude sensor: improvement of performance by filtering and sensor fusion}.
    \newblock Indian Institute of Astrophysics, Bangalore, India.

    \bibitem[Butta(2012)]{mag_noise}
    Butta, M. (2012).
    \newblock \emph{Sources of Noise in a Magnetometer Based on Orthogonal Fluxgate Operated in Fundamental Mode}.
    \newblock IEEE.

    \bibitem[Kleinbauer(2004)]{kalman_book}
    Kleinbauer, R. (2004).
    \newblock \emph{Kalman filtering implementation with Matlab}.
    \newblock Universität Stuttgart, Helsinki.

    \bibitem[Manoharan(2009)]{gps}
    Manoharan, S. (2009).
    \newblock \emph{On GPS Tracking of Mobile Devices}.
    \newblock University of Auckland, New Zealand.

    \bibitem[Ahmad et~al.(2013)]{imu_article}
    Ahmad, N., Ghazilla, R.~A.~R., and Khairi, N.~M. (2013).
    \newblock \emph{Reviews on Various Inertial Measurement Unit (IMU) Sensor Applications}.
    \newblock University of Malaya.

    \bibitem[Aronowitz(1971)]{fogs}
    Aronowitz, F. (1971).
    \newblock The laser gyro.
    \newblock In: Ross M., editor. \emph{Laser Applications}. Volume 1.
    \newblock Academic Press, New York, NY, USA.

    \bibitem[Sasiadek(2002)]{sensor_fusion}
    Sasiadek, J.~Z. (2002).
    \newblock Sensor fusion.
    \newblock \emph{Annual Reviews in Control}, 26(2):203--228.
    \newblock Department of Mechanical and Aerospace Engineering, Carleton University.

    \bibitem[Kalita(2014)]{sockets}
    Kalita, L. (2014).
    \newblock \emph{Socket Programming}.
    \newblock Department of Computer Science and Engineering, Assam Down Town University, Guwahati, India.

    \bibitem[Williams(2019)]{threads_williams}
    Williams, A. (2019).
    \newblock \emph{Język C++ i przetwarzanie współbieżne w akcji. Wydanie II}.

    \bibitem[{Gyroscope Technology}(2022)]{gyro}
    {Gyroscope Technology and Applications: A Review in the Industrial Perspective} (2022).
    \newblock \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5677445/}
    \newblock [Accessed: 21/11/2022].

    \bibitem[{Accelerometer}(2022)]{acceleromter}
    {Akcelerometr} (2022).
    \newblock \url{https://www.tme.eu/pl/news/library-articles/page/22568/Akcelerometr-jak-dziala-i-do-czego-sluzy/}
    \newblock [Accessed: 30/11/2022].

    \bibitem[{Sensor Noise}(2022)]{noise_generic}
    {Sensor Noise} (2022).
    \newblock \url{https://www.stemmer-imaging.com/en/knowledge-base/sensor-noise/}
    \newblock [Accessed: 11/11/2022].

    \bibitem[{Gazebo}(2022)]{gazebo_noise}
    {Sensor Noise Model} (2022).
    \newblock \url{https://classic.gazebosim.org/tutorials?tut=sensor_noise&cat=sensors}
    \newblock [Accessed: 12/11/2022].

    \bibitem[{Geographic Coordinates}(2022)]{geo_cords}
    {Współrzędne geograficzne} (2022).
    \newblock \url{https://pl.wikipedia.org/wiki/Wsp%C3%B3%C5%82rz%C4%99dne_geograficzne}
    \newblock [Accessed: 19/11/2022].

    \bibitem[{Compass Heading}(2022)]{magnetometer}
    {Compass Heading Using Magnetometers} (2022).
    \newblock \url{https://cdn-shop.adafruit.com/datasheets/AN203_Compass_Heading_Using_Magnetometers.pdf}
    \newblock [Accessed: 19/12/2022].

    \bibitem[{Differential Drive}(2022)]{diff_steering}
    {Differential Drive Kinematics} (2022).
    \newblock \url{https://www.cs.columbia.edu/~allen/F17/NOTES/icckinematics.pdf}
    \newblock [Accessed: 12/12/2022].

    \bibitem[{ROS Controllers}(2022)]{ros_controllers}
    {ROS controllers} (2022).
    \newblock \url{http://wiki.ros.org/ros_controllers?distro=noetic}
    \newblock [Accessed: 10/11/2022].

    \bibitem[{Ackermann Steering}(2022)]{ackermann_steering_controller}
    {Ackerman steering controller} (2022).
    \newblock \url{http://wiki.ros.org/ackermann_steering_controller?distro=noetic}
    \newblock [Accessed: 11/11/2022].

    \bibitem[{Diff Drive}(2022)]{diff_drive_controller}
    {Diff drive controller} (2022).
    \newblock \url{http://wiki.ros.org/diff_drive_controller?distro=noetic}
    \newblock [Accessed: 10/12/2022].

    \bibitem[{Gazebo Plugins}(2022)]{skid_steer_drive_controller}
    {Using Gazebo plugins with ROS} (2022).
    \newblock \url{https://classic.gazebosim.org/tutorials?tut=ros_gzplugins}
    \newblock [Accessed: 10/12/2022].

    \bibitem[{Twist Message}(2022)]{twist_msg}
    {Twist Message} (2022).
    \newblock \url{http://docs.ros.org/en/api/geometry_msgs/html/msg/Twist.html}
    \newblock [Accessed: 15/12/2022].

    \bibitem[{ROS Documentation}(2022)]{ros}
    {ROS Documentation main page} (2022).
    \newblock \url{http://wiki.ros.org/Documentation}
    \newblock [Accessed: 20/12/2022].

    \bibitem[{Kalman Filter}(2022)]{multi_kalman}
    {Multidimensional Kalman Filter} (2022).
    \newblock \url{https://www.kalmanfilter.net/kalmanmulti.html}
    \newblock [Accessed: 22/12/2022].

    \bibitem[{Actionlib}(2022)]{ros_actionlib}
    {Actionlib} (2022).
    \newblock \url{http://wiki.ros.org/actionlib}
    \newblock [Accessed: 23/12/2022].

    \bibitem[{ROS Services}(2022)]{ros_services}
    {Services} (2022).
    \newblock \url{http://wiki.ros.org/Services}
    \newblock [Accessed: 24/12/2022].

    \bibitem[{ROS Topics}(2022)]{ros_topics}
    {Topics} (2022).
    \newblock \url{http://wiki.ros.org/Topics}
    \newblock [Accessed: 25/12/2022].

    \bibitem[{RTOS}(2022)]{rtos}
    {Real-time operating system} (2022).
    \newblock \url{https://en.wikipedia.org/wiki/Real-time_operating_system}
    \newblock [Accessed: 26/12/2022].

    \bibitem[{Microservices}(2022)]{microservices}
    {Pattern: Microservice Architecture} (2022).
    \newblock \url{https://microservices.io/patterns/microservices.html}
    \newblock [Accessed: 27/12/2022].

    \bibitem[{Gazebo Simulator}(2022)]{gazebo}
    {Gazebo} (2022).
    \newblock \url{https://gazebosim.org/home}
    \newblock [Accessed: 28/12/2022].

    \bibitem[{URDF}(2022)]{urdf}
    {Urdf} (2022).
    \newblock \url{http://wiki.ros.org/urdf}
    \newblock [Accessed: 29/12/2022].

    \bibitem[{Ackermann}(2022)]{ackerman}
    {Ackerman Steering} (2022).
    \newblock \url{https://www.xarg.org/book/kinematics/ackerman-steering/}
    \newblock [Accessed: 30/12/2022].

    \bibitem[{XACRO}(2022)]{xacro}
    {XACRO} (2022).
    \newblock \url{http://wiki.ros.org/xacro}
    \newblock [Accessed: 31/12/2022].

    \bibitem[{XML Specs}(2022)]{urdf_xml}
    {XML Specifications} (2022).
    \newblock \url{http://wiki.ros.org/urdf/XML}
    \newblock [Accessed: 01/01/2023].

    \bibitem[{ROS Messages}(2022)]{types}
    {ROS messages} (2022).
    \newblock \url{http://wiki.ros.org/msg}
    \newblock [Accessed: 02/01/2023].

    \bibitem[{Digital Filters}(2022)]{filters}
    {Specjalne zastosowania filtrów cyfrowych} (2022).
    \newblock \url{https://sound.eti.pg.gda.pl/~greg/dsp/07-SpecjalneFiltry.html}
    \newblock [Accessed: 03/01/2023].

    \bibitem[{TCP/IP}(2022)]{tcpip}
    {Rodzina protokołów TCP/IP} (2022).
    \newblock \url{https://home.agh.edu.pl/~pmarynow/pliki/siec/is/TCP.pdf}
    \newblock [Accessed: 04/01/2023].

    \bibitem[{IMU}(2022)]{imu}
    {What Is An Inertial Measurement Unit} (2022).
    \newblock \url{https://www.vectornav.com/resources/inertial-navigation-articles/what-is-an-inertial-measurement-unit-imu}
    \newblock [Accessed: 05/01/2023].

    \bibitem[{Kalman 1D}(2022)]{kalman_1d}
    {Kalman Filter In One Dimension} (2022).
    \newblock \url{https://www.kalmanfilter.net/kalman1d.html}
    \newblock [Accessed: 06/01/2023].

    \bibitem[{Covariance}(2022)]{covariance}
    {A geometric interpretation of the covariance matrix} (2022).
    \newblock \url{https://www.visiondummy.com/2014/04/geometric-interpretation-covariance-matrix/}
    \newblock [Accessed: 07/01/2023].

    \bibitem[{Odometry}(2022)]{odometry}
    {Odometry} (2022).
    \newblock \url{https://docs.donkeycar.com/parts/odometry/}
    \newblock [Accessed: 08/01/2023].

    \bibitem[{AHRS}(2022)]{ahrs}
    {Inertial Labs.} (2022).
    \newblock \url{https://inertiallabs.com/ahrs.html}
    \newblock [Accessed: 09/01/2023].

    \bibitem[{NMEA}(2022)]{nmea}
    {Elektronika Praktyczna} (2022).
    \newblock \url{https://ep.com.pl/files/3937.pdf}
    \newblock [Accessed: 10/01/2023].

    \bibitem[{GPS Principles}(2022)]{gps_principles}
    {Principles of GPS} (2022).
    \newblock \url{https://www.gisresources.com/wp-content/uploads/2013/11/Principles-of-GPS-4-13-04.pdf}
    \newblock [Accessed: 11/01/2023].

    \bibitem[{Trilateration}(2022)]{trilateration}
    {The Math Behind GPS} (2022).
    \newblock \url{https://letstalkscience.ca/educational-resources/backgrounders/math-behind-gps}
    \newblock [Accessed: 12/01/2023].

    \bibitem[{Magnetometer Basics}(2022)]{magneto_work}
    {Magnetometer basics for mobile phone applications} (2022).
    \newblock \url{http://www.nicap.org/madar/smart_phones/Magnetometer_Basics_For_Mobile_Phone_Applications-2012.pdf}
    \newblock [Accessed: 13/01/2023].

    \bibitem[{Visual Odometry}(2022)]{odom_2}
    {Review of visual odometry: types, approaches, challenges, and applications} (2022).
    \newblock \url{https://link.springer.com/article/10.1186/s40064-016-3573-7}
    \newblock [Accessed: 14/01/2023].

    \bibitem[{Synchro Drive}(2023)]{sync_drive}
    {Robo-Rats Locomotion: Synchro Drive} (2023).
    \newblock \url{https://groups.csail.mit.edu/drl/courses/cs54-2001s/synchro.html}
    \newblock [Accessed: 15/01/2023].
\end{thebibliography}
